% (This file is included by thesis.tex; you do not latex it by itself.)

\begin{abstract}

% The text of the abstract goes here.  If you need to use a \section
% command you will need to use \section*, \subsection*, etc. so that
% you don't get any numbering.  You probably won't be using any of
% these commands in the abstract anyway.

The Asian summer monsoon supplies around 3 billion people with much of their yearly supply of freshwater, necessary for human consumption as well as in agriculture and industry. In many regions, particularly along the Ganges River in India and in northern China, use of freshwater far exceeds natural recharge rates. Given the high population density of these regions, a substantial fraction of Asia's population is therefore critically sensitive to changes in the supply of freshwater by the monsoon under 21st century warming. A first step toward future projection is to consider the available observational record of rainfall. This dissertation focuses on the leading mode of Asian Monsoon rainfall variability (All-Asia EOF1) which links two major subsystems: the South Asian and East Asian monsoons.

In summer, two distinct rainfall rÈgimes are observed: Convective storms over India, Bangladesh and Nepal (the South Asian monsoon), and frontal rainfall over China, Japan and Korea (the East Asian monsoon). In addition, the Himalayas and other orography, including the Arakan Mountains, Ghats and Yunnan Plateau, create smaller precipitation domains separated by sharp gradients. My research has revealed a previously unrecognized mode of continental precipitation variability that spans both South and East Asia during July and August. A dipole between the Himalayan Foothills and the ÄúMonsoon ZoneÄù of central India dominates July-August interannual variability in South Asia, and is also associated in East Asia with a tripole between the Yangtze Corridor and North and South China. By performing lag-lead correlation of rainfall, I show that this covariation does not correspond to the spatial pattern of July-August storm tracks. Instead, I hypothesize that interannual change in the strength of moisture transport from the Bay of Bengal to the Yangtze Corridor across the northern Yunnan Plateau induces widespread precipitation anomalies. Abundant moisture transport along this route requires both cyclonic monsoon circulation over India and sufficient heating over the Bay of Bengal, which occurs only during July and August, as I also show by analyzing existing runs with a zoomed, nested version of the LMDZ5 model nudged to reanalysis.

In China, a growing body of work identifies a rÈgime shift in rainfall occurring in the late 1970s known as the ``South Flood-North Drought.'' However, this phenomenon has not previously been described in terms of the complex seasonal cycle of the East Asian monsoon. During the peak interval of rainfall, known as Meiyu season, a persistent but meandering front (the ``ÄúMeiyu Front''Äù) delivers strong bouts of rainfall over a narrow latitude band. The preferred latitude of this front shifts throughout the year and shifts abruptly from May to July. I have developed an image processing algorithm that produces a 57-year (1951-2007) daily catalog of frontal rainfall events in China, reporting its latitude, intensity and coherence. This result allows for a quantitative assessment of Meiyu change between 1951-1979 and 1980-2007, which has never previously been performed on an event-by-event basis. I find that the greatest change in frontal behavior has occurred during May, when events have strongly decreased over the Yangtze River valley. In addition, a statistically significant southward shift has occurred in July-August Meiyu events. Both of these months have also witnessed a southward displacement in the latitude of the tropospheric jet toward the end of the 20th century. Thus, I propose the novel hypothesis that the ``ÄúSouth Flood-North Drought'' can be attributed to a change in the timing and extent of the tropospheric jet'Äôs meridional transit.

All-Asia EOF1 not only describes a key mode of Asian monsoon variability but is also associated with climate anomalies across the entire Northern Hemisphere. This resembles a previously studied summer pattern known as the Circumglobal Teleconnection (CGT), a high-latitude standing wave pattern with wavenumber 5 or 6. JRA-55 captures the changes in water vapor transport across the Yunnan Plateau hypothesized in Chapter 2, and also suggests that they induce a pattern a monsoon-desert-type pattern of diabatic heating between the Himalayan Foothills and Yangtze River Valley and cooling to the west. We propose that the particular topography of the Yunnan Plateau plays a role in the phase-locking of the CGT. Over China and East Asia, the variability of All-Asia EOF1 appears as a meridional jet shift. Using the RDA catalog from Chapter 3, we find that the South Flood-North Drought robustly corresponds to a southward shift in the East Asian tropospheric jet., known to be chaotic at the monthly scale, may nonetheless be improved by further studying the effect of twenty-first-century global warming on moisture transport from the Bay of Bengal to the Yangtze Corridor and the East Asian jet.

\end{abstract}
