\chapter{Introduction}

\blockquote{
%
%	``On the day the monsoon began, I was swimming in the river with a dozen other young men and about twenty children. The dark clouds, which had painted their sombre moods on the sky for weeks, gathered from horizon to horizon, and seemed to press upon the tops of the tallest trees. The air, after eight dry months, was so lavishly perfumed with rain that we were almost drunk with excitement.
%	
%	`Paous alla! S'alla ghurree!' the children cried repeatedly, grasping my hands. They pointed to the clouds and dragged me toward the village. `The rain is coming! Let's go home!'
%	
%	The first drops of rain fell as we ran. In seconds, the drops were a heavy fall. In minutes, the fall was a cascade. Within an hour, the monsoon was a ceaseless torrent, so thick that it was difficult to breathe in the open without cupping my hands to my mouth to make a little cave of air.
%	
%	At first, the villagers danced in the rain and played pranks on one another. Some took soap, and washed in the heaven-sent shower. Some went to the local temple, where they knelt in the rain to pray. Others busied themselves with repairs to the roofs of their houses and the drainage trenches dug around every mud-brick wall.
%	
%	Eventually, everyone stopped to simply stare at the drifting, flapping, curling sheets of rain. Every doorway of every house was crowded with faces, and each flash of lightning showed the frozen tableaux of wonder.
%	
%	That downpour of several hours was followed by a lull just as long. The sun shone intermittently, and rainwater steamed from the warming earth. The first ten days of the season proceeded in the same way, with violent storms and tranquil lulls, as if the monsoon was probing the village for its weaknesses before mounting a final assault.
%	
%	Then, when the great rain came, it was a lake of water in the air, and it rained almost without pause for seven days and nights. On the seventh day, I was at the river's edge, washing my few clothes as the drenching torrents fell. At one point I reached for my soap, and realised that the rock I'd place it on was submerged. The water, which had merely caressed my bare feet, rose from my ankles to my knees in seconds. As I looked upstream at the tumbling crash of the river, the water reached to my thighs, and was still rising.
	`The river! The river is coming!' I shouted, in broken Marathi.

	Sensing my distress but not really understanding me, the villagers gathered around and then called Prabaker, plying him with questions.
	
	`What is your matter, Lin? The people are very upset for you.'
	
	`The river! It's coming up fast. It'll wipe the village out!'
	
	Prabaker smiled.
	
	`Oh, no, Lin. That will not be happening.'
	
	`I'm telling you! I've seen it. I'm not joking, Prabu. The fucking river's in flood!'
	
	Prabaker translated my words for the others. Everyone laughed...
	
%	`Are you all crazy?' I shouted, in exasperation. `It's not funny!'
%	
%	They laughed all the harder and crowded around me, reaching out to calm my fear by patting and stroking me, their laughing voices full of soothing words and sighs. Then, with Prabaker leading the way, the crowd of villagers goaded, dragged and pushed me toward the river.
	
	The river, only a few hundred meters away, was a deluge: a vast muddy concrescence that tore through the valley in heaving waves and boiling eddies. The rain redoubled its intensity as we stood there, our clothes as drenched as the yielding soil. And still the tumid river grew, consuming new land with each thumping heartbeat.
	
	`You see those sticks, Lin,' Prabaker said, in his most irritating attempt at a soothing tone. `Those sticks are the flood-game sticks. Do you remember, when the people put them in the ground? Satish and Pandey, Narayan and Bharat...do you remember?'
	
%	I did remember. Days before, there'd been a lottery of some kind ... 
%	
%	One hundred and twelve numbers - one for every man in the village - were written on small pieces of paper, and mixed together in an empty clay water-pot, called a matka. The men lined up to draw their numbers, and then a second set of the same numbers was mixed in the pot. A little girl was given the honour of drawing the six winning numbers from the pot. The whole village watched the ceremony, and applauded the winners happily.
%	
%	The six men whose numbers had been drawn had won the chance to hammer a wooden stake, a little over a metre long, into the earth. As well, the three oldest men in the village were accorded the right to a wooden stake without the numbered lottery. They duly chose places for their stakes, and younger men obliged by hammering the wooden pegs into the ground. When all nine stakes were positioned, little flags with the names of the men were tied to each one, and the people drifted back to their homes.
%	
%	I'd watched the affair from a shady spot beneath the branched dome of a tree. At the time, I was working on my own small reference dictionary of the Marathi language, based on phonetic spellings of the words I heard every day in the village. I gave the ceremony little attention, and I never bothered to ask its purpose.
	
	I did remember. Days before, there'd been a lottery of some kind ... As we stood in the numbing, drumming rain and watched the prowling advance of the river, Prabaker explained that the wooden stakes were part of a flood-game that was played every year. The oldest men in the village, and six lottery winners, were given the chance to predict the point to which the river would rise. Each wooden stick, with its flag of yellow silk, represented a best guess.
	
	`You see, this one little flag?' Prabaker asked, pointing to the stake that was furthest from where we stood. `This one is almost gone. The river will reach to him, and cover him, tomorrow or tonight.' 
	
	He translated what he'd told me for the crowd, and they pushed Satish, a heavy-set cowherd, to the front of the group. The almost submerged stick was his, and he accepted, with shy laughter and downcast eyes, the good-natured jeers of his friends and the sneers of the older men.
	
	`And this one here,' Prabaker went on, pointing to the stake nearest to our position. `This one is the river will never be touching. The river never comes more far than this place. Old Deepakbhai has picked for himself this place, for the putting of his stick. He thinks this year will be a very heavy monsoon ...'
	
%	The villagers had lost interest, and were already drifting or jogging back to the village. Prabaker and I stood alone.
	
	`But ... how do you know that the river won't rise past this point?'
	
	`We are here a long time, Lin. Sunder village has been in this place for two thousands of years. The next village, Natinkerra, has been there for much longer, about three thousands of years. In some other places - not near to here - the people do have a bad experiences, with the floods, in monsoon time. But not here. Not in Sunder. Our river has never come to this far. This year, also, I don't think it will come to this far, even so old Deepakbhai says it will. Everybody knows where the river will stop, Lin.'
	
	\attrib{Gregory David Roberts, \textit{Shantaram}, 133-135}}
	
	Clearly, atmospheric dynamicists are not the only ones to engage in the art of monsoon prognostication. Nonetheless, in spite of a century of work, forecasts of present-day monsoon seasonal variability and of future changes under global warming remain nebulous. The purpose of this dissertation is to elucidate the atmospheric dynamics implicated with the leading mode of Asian summer monsoon variability and reveal connections to other important modes of climate variability. The ultimate vision is that increasingly skillful projections of these other climate components will also be used to improve projection of changes in the \nth{21} century monsoon.

	An overview of the current consensus on monsoon dynamics and other information on the spatiotemporal variability of rainfall in the Asian monsoon are presented in the introduction to Chapter 2. Instead, I include here short overviews of several topics that are not addressed in any of the following chapters: the history of the monsoon on paleoclimatic timescales, human impacts of monsoon variability, and the consensus of current projections on the future of the monsoon. These are not intended to be exhaustive reviews, but rather background information that justifies the importance of the material in following chapters.
	
\section{The Asian Paleomonsoon}

	The study of rainfall variability in the Asian monsoon suffers from the limited duration of available records. Satellite observations provide an even spacial distribution of rainfall as well as instantaneous snapshots of the same region at different points in its diurnal cycle. The satellite record has continued to expand thanks to the unexpected longevity of the Tropical Rainfall Measuring Mission (TRMM) and the relatively recent Global Precipitation Measurement (GPM) satellite, but unfortunately extends back only to 1997. Instead, we rely on rain gauge data for decadal time series, assembled from daily collection of precipitation at weather stations around the globe, often with very basic apparatus. Unlike satellite observations, records are available only over land and are highly heterogeneous with space and time, and also subject to observational errors. Data sets such as APHRODITE, a rain gauge data set focused on the Asian monsoon region, attempt to weed oust spurious observations with quality control algorithms and then present users with a refined product \citep{Yatagai2012}. This dissertation could not have been written without the efforts of APHRODITE's compilers; they are further acknowledged in subsequent chapters.
	
	We would also like to consider how the monsoon operates under substantially altered climates. The planet is on the verge of reaching a global mean temperature unseen in recent Earth history, and it could be useful to have information on how the monsoon behaved under altered insolation conditions, and how much it can be perturbed from its present form in general. Fortunately, remarkable records exist that can provide information about rainfall on a precessional time scale: cave speleothems, which are stalagmites featuring tens of thousands of years of continuous deposition\footnote{At some sites such as in Oman, stalagmite deposition is intermittent, also taken as an indicator of paleomonsoon change \citep{Burns2001,Fleitmann2003}.} from which a $\delta ^{18}O$ time series can then be compiled, often by stitching together records from multiple stalagmites. Since 2001, dozens of speleothem sites have been developed across East and South Asia, particularly in the East Asian monsoon region \citep{Wang2001,Dykoski2005,Wang2008b}, but also near the Tibetan Plateau \citep{Cai2010b}, Yunnan Plateau \citep{Cai2015}, Altay Mountains\citep{Cheng2012} and numerous other locations. There are fewer of such records in India, partially because caves are often holy sites in local folklore.
	
	Beyond the difficulty in obtaining such records, their interpretation poses a major challenge. East Asian speleothem $\delta ^{18}O$ records tend to feature remarkable agreement across thousands of kilometers, most notably demonstrating simultaneous abrupt transitions on the time scale of precessional forcing \citep{Chiang2015}. Past authors have interpreted these coherent changes as variations in Asian monsoon ``intensity'', and therefore local rainfall \citep{Wang2001,Liu2014}, based on the concept of the ``amount effect'' wherein the $\delta ^{18}O$ of precipitation from a parcel will decrease over time as heavier isotopes rain out, a process referred to as Rayleigh distillation \citep{Dansgaard1964}. 
	
	However, in present day observations, the climatological distribution of precipitation $\delta ^{18}O$ is poorly explained by Rayleigh distillation, and furthermore monthly variations in precipitation $\delta ^{18}O$ across China are poorly correlated with local precipitation and temperature \citep{Dayem2010,Lee2012}. Instead, China $\delta ^{18}O$ is weakly correlated with Indian monsoon rainfall amounts upstream \citep{Lee2012}. Therefore, recent interpretations have turned to alternative mechanisms, such as changes in moisture source region, variations in Indian monsoon rainfall intensity and changes in transport pathway \citep{Maher2008,Dayem2010,Pausata2011,Baker2015}. That being said, no single theory has explained the abrupt jumps in East Asian speleothem records in a fully satisfactory way, or proven whether they correspond to abrupt changes in Asian monsoon rainfall or not.
	
	On a time scale of millions to tens of millions of years, the Asian monsoon region can be viewed as a geophysical fluid dynamics laboratory. The Tibetan Plateau rose to its full height of 5,000+ meters some time in the past 50 Ma after the collision of the Indian sub-continent, with massive climate impacts. Based on geological evidence, it was previously proposed that a surge in Tibetan Plateau elevation around \mytilde10 Ma may have triggered a sudden intensification of the Indian monsoon \citep{Harrison1992,Molnar1993}. However, recent work suggests that a sudden jump in preserved \textit{G. bulloides} deposits in the Arabian Sea around 8.5 Ma, previously attributed to monsoon intensification, likely resulted instead from uplift of the Indian Ocean seafloor \citep{Rodriguez2014}. In addition, theoretical studies suggest that a strong monsoon should exist as long as there remains a region of strong off-equatorial heating, provided by the presence of the Indian subcontinent since 50 Ma \citep{Prive2007a,Bordoni2008,Molnar2010}. 
	
	One other intriguing multi-million year record exists: northern China's Loess Plateau, the longest continuous depositional basin on the planet. By preserving millions of years of silt and dust from surrounding deserts and the rest of the Northern Hemisphere, the Loess Plateau stores invaluable information about paleoclimate and in particular glacial-interglacial cycles, since the planet tends to be dustier during glacials \citep{Sun2006}. However, like the speleothem records, its interpretation remains a point of contention \citep{Roe2009}.

\section{Human Impacts}

	In summer, monsoonal regions experience bouts of steady, heavy rainfall interspersed by occasional ``breaks,'' and much drier conditions during the rest of the year. In many parts of Asia, this yearly supply is used to grow two crops per year; in India, these two crops are the summer \textit{kharif} and the winter \textit{rabi}, both of whose fruition depends on rainfall supply from the monsoon \citep{Gadgil2006a}. The majority of Indian land in the 2000s remained unirrigated and depended directly on rainfall \citep{KrishnaKumar2004}. Therefore, the timing and intensity of the summer monsoon control agricultural outcomes.
	
	An early or delayed Indian monsoon onset can interfere with the transplantation of rice seedlings from their nursery beds \citep{Gadgil2006a}. Most Indian crop yields are correlated with June-September All-India monsoon rainfall above a 99\% confidence level \citep{KrishnaKumar2004}, and severe drought All-India Monsoon Rainfall years were found to induce cuts to Indian GDP of 2-5\% \citep{Gadgil2006}. Aside from agriculture, extreme rainfall events can inflict massive damages through flooding \citep{Li2012}. The research literature estimating damages from monsoon-season flooding is sparse, although studies of cyclones find that long-term mortality can exceed immediate mortality by an order of magnitude \citep{Anttila-Hughes2012}, and that countries experiencing \nth{90} percentile cyclone events  suffer from a per-capita income reduction of 7.4\% 20 years later versus a scenario where the event did not happen \citep{Hsiang2014}.
	
	It can be challenging to interpret the historical record of the past fifty years because humans have induced not only warming due to increasing CO$_2$ but also massive anthropogenic forcing from emissions of NO$_x$, black carbon and other aerosols. It is estimated that high levels of near-surface ozone due to human activity lower India's crop yields by 9\% each year, enough to feed roughly 94 million people \citep{Ghude2014}, and that all noxious emissions combined induce a 36\% decline in wheat yields \citep{Burney2014}. The massive injection of aerosols to East Asia also reduced the amount of insolation directly reaching the surface from 1961 to 1980 (so-called ``solar dimming'') and increased slowly while the rest of the planet has experienced a solar ``brightening'' \citep{Norris2009}. Over the 2000s in China, reduction of incoming shortwave radiation by aerosols at the surface was found to be $-15.7 \pm 8.9$ W m$^{-2}$ nationwide, and reached $-61.2 \pm 3.5$ W m$^{-2}$ locally in Beijing \citep{Li2010b}. Observed climate change in China over the past half-century has been blamed on both aerosols and warming with no clear consensus \citep{Menon2002,Yang2015,Yu2016,Yang2016}.
	
\section{\nth{21} Century Projections}

	The water vapor content of the atmosphere obeys the Clausius-Clapeyron relation and will increase at a rate of roughly 7\% per $^{\circ}$C of warming. The size and intensity of storms is fundamentally constrained by the available supply of water vapor \citep{Trenberth2003}. However, models consistently project a slower rate of increase of about 2-3\%/$^{\circ}$C \citep{Allen2002}, potentially due to a slowdown in the overturning circulation in the Hadley Cells \citep{Held2006}. The distribution of changes is highly heterogeneous, roughly obeying a ``rich get richer'' distribution where convective regions become rainier and arid regions drier \citep{Chou2009}. However, particular regions may experience abrupt transitions under further warming, for instance via the template of ``convective margin'' shifts \citep{Lintner2007}. Both shifts in mean and in the tails of the distribution need to be characterized \cite{Pendergrass2014b}. Theory and idealized models suggest that the globally averaged rainfall extremes will increase at roughly 4\% per $^{\circ}$C, more than the rate of increase of mean rainfall but still below Clausius-Clapeyron, and that rainfall extremes may increase more rapidly in the Tropics \citep{Ogorman2009,Muller2011a,OGorman2012}.
	
	Future changes in monsoon rainfall may conform to simple templates such as the rich-get-richer, but the distribution of topography across the Asian monsoon may also make its response unique. For instance, it has been argued that the circulation response to Indo-Pacific warm pool heating has led to an overall drying of South Asia \citep{Annamalai2013}. Examining the past 50 years, \citet{Turner2012} suggested that anthropogenic aerosols countered an increase in rainfall due to increased CO$_2$ that would have been anticipated in most models. Some authors have speculated that the monsoon could undergo an abrupt r\'{e}gime shift \citep{Zickfeld2005}, while others project a linear increase in rainfall with warming \citep{Boos2016}. In models simulating increased CO$_2$ conditions, \citet{Chen2016} decomposed future East Asian rainfall changes  into a fast and slow component of response, and found that the two terms were of opposite sign, with long-term warming and rainfall increase due to heightened sea surface temperature eventually prevailing over a short-term cooling and rainfall decrease due to circulation change.
		
	Many have begun to investigate the impact of future warming on agriculture and economy. Rising nighttime temperature has been indicated as a threat to agricultural productivity, decreasing yields by as much as 10\%/$^{\circ}$K \citep{Peng2004}. Many crops are found to have a critical temperature, wherein yields will rise steadily up until that temperature and then decline severely if it is exceeded \citep{Schlenker2009}. In Indonesia, global warming in the IPCC4 model suite was suggested to raise the probability of a 30-day delay in monsoon initiation from 9-18\% to 30-40\% by 2050 \citep{Naylor2007}. \citet{Auffhammer2012} found that agricultural productivity in India was 4\% lower during 1966-2002 had monsoon conditions from 1960 persisted through that era. A novel literature focuses on linking climate more directly to human impacts. For instance, \citet{Burke2015} showed that economic productivity is nonlinear with temperature across the globe, with peak productivity occurring at 13$^{\circ}$C and decreasing nonlinearly at higher temperature. \citet{Hsiang2014} suggested that previous estimates of the total cost of global warming had undercounted by \$9.7 trillion by neglecting the full economic damage from cyclones under warmer conditions. The field is ripe for the application of such techniques to the South Asian and East Asian monsoon regions, but to our knowledge no efforts to date have focused specifically on those regions.

\section{Thesis Structure}

	Chapter 2 presents an analysis of observational evidence from rain gauge precipitation data suggesting that a link exists between interannual variability in the South Asian and East Asian monsoons, and studies the propagation of rainfall anomalies on a daily scale to see if this reproduces leading modes of monthly variability. We propose that the variability of the two monsoons is linked by monthly variations in moisture transport from the Bay of Bengal to the Yangtze River valley across the Yunnan Plateau, a spur of terrain to the southeast of the Tibetan Plateau. Dynamical theory and preliminary model data support major elements of this theory. These results were previously presented in \citep{Day2015}.

	Chapter 3 develops the Rainband Detection Algorithm (RDA), a recursive image processing tool to analyze daily patterns of frontal rainfall in China. We discover that banded rainfall contribute a large fraction of yearly total precipitation to Central China and describe the seasonal progression of banded rainfall. Our algorithm also allows a novel characterization of the South Flood-North Drought, a known pattern of decadal change wherein central China has experienced increased rainfall and northern China severe droughts beginning in the 1980s. Most notably, rainbands have become \textit{less frequent} in May and \textit{shifted southward} in July-August. Finally, we show that the pattern of decadal change in yearly rainfall totals is due specifically to change in banded rainfall.

	Lastly, Chapter 4 returns to the leading mode of Asian summer rainfall variability and shows robust links with two other important climatic components: The Circumglobal Teleconnection, a high-wavenumber Northern Hemisphere standing wave responsible for heat waves, and the East Asian tropospheric jet. Using JRA-55 reanalysis data, we find that changes in westerly moisture transport across the Yunnan Plateau drive a zonal band of heating spanning the Himalayan Foothills and Yangtze River valley, which we propose can then stimulate the CGT mode and contributes to its phase-locking. Also associated with these changes are meridional shifts of the East Asian jet. Using the RDA catalog from Chapter 3, we are able to show that the two major changes in rainbands associated with the South Flood-North Drought also corresponded to southward shifts of the East Asian jet. We suggest that these findings have the potential to improve projection of the \nth{21}-century Asian monsoon. 

\section{Future Directions}

	Studying rainfall is intrinsically challenging because correlation length scales are short relative to other atmospheric fields. Rainfall results from ascent, which is in turn the residual of much larger-magnitude differences in wind fields. Thus, reproducing its distribution in a computer model presents a massive challenge. The advent of high resolution global climate modeling (below $1^{\circ} \times 1^{\circ}$) will therefore change how we can analyze rainfall patterns in the  Asian monsoon. Existing studies already show that low, narrow orographic barriers greatly impact the monsoon's climatology \citep{Xie2006}. Studies with high resolution to date already show that resolving low topography and high-resolution features can alter the hydrologic balance and circulation of the monsoon \citep{Risi2010,Boos2013a,Wu2014a,Wu2016}. A central claim of this dissertation is that moisture transport across the Yunnan Plateau couples the variability of the South Asian and East Asian monsoons. The existence of high-resolution global climate modeling now allows us to test this hypothesis with idealized scenarios. What would happen to moisture transport from South Asia to East Asia, or alternatively if there were no high topography southeast of the Tibetan Plateau at all? Without computer modeling we struggle to distinguish the ultimate stimulus from the response; we can now test whether moisture transport from the Bay of Bengal can provide a plausible trigger for intense diabatic heating over the Yangtze River valley, and furthermore whether such heating can drive a CGT-like response.
		
	The holy grail remains a robust projection for what will happen to the Asian monsoon under further warming. Although the CMIP5 suite from the IPCC5 report consistently predicts a stronger Indian monsoon, it is not clear that individual models can simulate the mean state of the Indian monsoon well. This is an even larger problem with the East Asian monsoon, where almost none of the CMIP5 models can produce a climatology that looks like the series of northward transitions of the Meiyu front. My work in this dissertation focuses on particular mechanisms that are important to the rainfall variability of the South Asian and East Asian monsoons, in particular the East Asian jet, the CGT and moisture transport across the Yunnan Plateau. I argue that these mechanisms are more likely to be captured by models because their spatial scale is larger and they lack the heterogeneity over short distances that is intrinsic to rainfall patterns. Given this belief, the best way forward on predicting the future Indian and East Asian monsoon may be to focus on the effects of further warming on each of these climate components individually, and then to deduce later what alterations they may produce in the seasonal cycle of the South and East Asian monsoons.
	
	Lastly, our growing knowledge of the fluid dynamics of the East Asian monsoon should be turned back to the paleoclimate record. \citet{Chiang2015} found a novel way to juxtapose our knowledge of present-day dynamics with the analysis of speleothems by considering the $\delta ^{18}O$ of rainfall during different Meiyu stages, and considering what the isotopic signature would be if the timing of those stages was altered. Given our improving knowledge of different East Asian monsoon stages and the ability to model them reasonably, we should discard the idea of a coherent East Asian monsoon ``intensity." Instead, we ought to focus on describing changes in rainfall during specific Meiyu stages under altered climates and the $\delta ^{18}O$ variations that should result. In addition, the interpretation of the Loess Plateau should be revisited. Its first appearance is often interpreted as the timing of initiation of the East Asian monsoon. However, , I suggest that the rise of the Altay Mountains north of the Taklamakan Desert may be a more likely candidate for the trigger of the Loess Plateau's creation, since the presence of the Tibetan Plateau after 50 Ma likely also entails an East Asian monsoon. Given the ability to model jet shifts induced by transient forcing \citep{Liu2012}, we may be able to say something more specific about the change in circulation that first gave rise to the Loess Plateau.